---
title: "Exploring Limit Theorems (LLN & CLT)"
output: pdf_document
---

# 1. Introduction
This project explores two fundamental statistical theorems:
- Law of Large Numbers (LLN)
- Central Limit Theorem (CLT)
using Monte Carlo simulations in R.

We analyze convergence behavior and distributional properties.

---

# 2. Theory

## 2.1 Law of Large Numbers
The sample mean converges to the expected value as n increases.

## 2.2 Central Limit Theorem
The distribution of standardized sample means converges to a normal distribution.

---

# 3. CLT Simulations

```{r}
source("R/IDS3_Project/functions/clt_functions.R")

means <- simulate_clt("exp", 30, 10000)
plot_clt(means, "CLT - Exponential (n=30)")
```

# 4. LLN Simulation

```{r}
source("R/IDS3_Project/functions/lln_functions.R")

values <- rexp(1000)
plot_lln(values, 1, "LLN - Exponential")
```

# 5. Conclusion

LLN shows convergence of averages
CLT shows emergence of normality
Results confirm theoretical predictions

# 6. Discussion

The results confirm that:

- Increasing sample size reduces variance (CLT effect)
- Sample means converge to expected value (LLN effect)
- Even skewed distributions (Exponential) become normal under CLT

This demonstrates the universality of the normal distribution in statistics.